\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage{pst-all}
\usepackage{hyperref}
\usepackage[hidelinks]{hyperref}
\usepackage{float}
\usepackage{xfrac}
\usepackage{longtable}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{url}
\usepackage{bbm}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{mwe}
\usepackage{breqn}
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}

\makeatletter
\renewcommand*\env@matrix[1][c]{\hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{*\c@MaxMatrixCols #1}}
\makeatother

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\lstset{
  basicstyle=\ttfamily,
  mathescape
}
\setlength{\belowcaptionskip}{-0.2cm}
\arraycolsep=1.4pt
\def\arraystretch{2} 
\usepackage{mathtools}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\title{Analysis of fractional-order system for financial dynamics}
\let\iif\leftrightarrow
\author[1]{Mateo Restrepo Sierra}
\author[2]{Juan S. C\'ardenas Rodr\'iguez}
\author[3]{David Plazas Escudero}
\affil[1]{Universidad EAFIT, mrestrepos@eafit.edu.co, Student, Medell\'in, Colombia}
\affil[2]{Universidad EAFIT, jscardenar@eafit.edu.co, Student, Medell\'in, Colombia}
\affil[3]{Universidad EAFIT, dplazas@eafit.edu.co, Student, Medell\'in, Colombia}
\keywords{Macroeconomic financial system, fractional-order system, chaos, stability, feedback control, Adams-Bashforth-Moulton algorithm.}

 \begin{abstract}
	This work studies the Huang-Li financial nonlinear dynamic system, based on Chen's generalization: the given system can be also studied for non-integer order differential equations. This approach is based on two main facts that involves financial systems: chaos and memory. In one hand, it can be shown that the dynamic system in study is indeed a chaotic system; on the other hand, as financial systems are highly correlated with previous events, memory is essential, hence the use of fractional derivatives. A stability analysis and control were performed. This work is intended to give a more detailed version of the procedure mentioned in Chen's paper, since all simulation parameters for the system are specified and we include a short comparison between the numerical procedures. It was found that the system is highly controllable in both equilibrium points and periodic orbits; the stability of some points is strongly dependent on the system's order. On the other hand, a sensitivity analysis was done based on methods described on the literature and it was found that the system is sensitive to different parameters depending on the order.
 \end{abstract}
\begin{document}

\flushbottom
\maketitle

\thispagestyle{empty}

\input{text/1_intro}
\input{text/2_method}
\input{text/3_result}
\input{text/4_stability_control}
\input{text/5_sensitivity}
\input{text/6_conc}
%Bibs
\bibliographystyle{ieeetran}
\bibliography{ref}


\end{document}
