\section{Preliminaries}\label{sec:pre}
\subsection{ARMA Model}
The general scheme for the observer-ARMA model is given by
\begin{equation}
  \begin{split}
    &z_{t+1}=\sum_{s=0}^{l_1}a_sz_{t-s}+\sum_{s=0}^{l_2}b_s\xi_{t-s}\\
    &y_t=h_tz_t+\zeta_t\\
    &z_0\in\R, \ t=0,1,\dots
  \end{split}
\end{equation}

\subsection{The Kalman-Filter State-Observer Model}
Every ARMA model can be translated into a KF state-observer model, given by
\begin{equation}\label{eq:kf_so}
  \begin{split}
    &x_{t+1}=F_tx_t + \xi_t\\
    &y_t=H_tx_t+\zeta_t\\
    &x_0\in\R^n, \ t=0,1,\dots
  \end{split}
\end{equation}

\subsection{Extended KF}
The main idea behind the extension is to apply the standard KF in nonlinear systems. Let us consider a system in the form
\begin{equation}
  \begin{split}
    &x_{t+1}=f(x_t) + \xi_t\\
    &y_t=H_tx_t+\zeta_t\\
    &x_0\in\R^n, \ t=0,1,\dots
  \end{split}
\end{equation}
where $f:\R^n\rightarrow\R^n$ is a given vector function. In order to apply the KF, we wish to linearize the function $f(\cdot)$ around a reference point $x^{{\rm ref}}_t$, following the common linearization scheme using the jacobian of $f(\cdot)$.

Let
\[
\tilde{F}_t:=\dfrac{\partial f(x)}{\partial x}\bigg|_{x=x^{{\rm ref}}_t}
\]
with $\tilde{F}_t$ model (\ref{eq:kf_so}) can be constructed and applied to the KF.

\subsection{ILS?}





\section{Instrumental Extended KF}\label{sec:IEKF}
In this work we will use a simple ARMA model, with correlated state and one unknown stationary parameter $a$. The model in consideration is
\begin{equation}
  \begin{split}
    &z_{t+1}=az_t+\xi_t+d\xi_{t-1}\\
    &y_{t}=hz_t+\gamma_{t}
  \end{split}
\end{equation}
and the objective is find an estimator $\tilde{a}$ for the unknown parameter $a$ using the data vector $y^*_t$.

First, we assume that $\tilde{a}$ is not a constant, even when the real paramater $a$ is stationary. This assumption takes into consideration that the data vector can be constantly changing and the estimation will change depending on each observation. Another important assumption is that this estimator $\tilde{a}_t$ has small linear changes, hence, this estimator takes the form
\begin{equation}
  \tilde{a}_t=b\tilde{a}_{t-1}+\chi_{t-1}
\end{equation}
with $0<b<1$ and $\chi_t \sim N(0,\,\sigma)$. Given the dynamics for $\tilde{a}_t$, we propose the complete dynamics for the ARMA model as
\begin{equation}
  \begin{split}
    &z_{t+1}=\tilde{a}_tz_t+\xi_t+d\xi_{t-1}\\
    &\tilde{a}_{t+1}=b\tilde{a}_t+\chi_t\\
    &z_0\in\R,\,\tilde{a}_0\in\R,\,t=0,1,\dots
  \end{split}
\end{equation}
Note that the dynamics have a nonlinear, particularly bilinear, term in the first equation. Let $x_t:=(z_t,\,\tilde{a}_t)^T$ and let $x^{{\rm ref}}_t:=(z_t^{{\rm ref}},\,\tilde{a}_t^{{\rm ref}})^T$ be a given reference point, the linearization yields the matrix
\[
\tilde{F}_t = \begin{bmatrix}
\tilde{a} & z\\
0 & b
\end{bmatrix}_{x=x_t^{{\rm ref}}}
\]
and the previously described KF scheme can be applied.
