\documentclass[11pt]{article}
\usepackage[english]{babel}
\input{commands.tex}

%%%%%%%% MARGIN
\geometry{verbose, letterpaper, tmargin=3cm,
  bmargin=3cm,lmargin=2.5cm,rmargin=2.5cm}

%%%%%%%% PARAGRAPH SETTINGS
% https://bit.ly/36WrtN4
\setlength\parindent{0pt}

% https://bit.ly/371dvto
\setlength{\parskip}{5pt}

%%%%%%%% HYPERREF PACKAGE
\usepackage{hyperref}
\hypersetup{linkcolor=blue}
\hypersetup{citecolor=blue}
\hypersetup{urlcolor=blue}
\hypersetup{colorlinks=true}


%%%%%%%% DEFINITION AND THEOREM DEFINITIONS
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\theoremstyle{remark}
\newtheorem{question}{Question}

\newtheorem{theorem}{Theorem}[section]

%%%%%%%% ENUMERATE LABEL
% https://www.latex-tutorial.com/tutorials/lists/
\usepackage{enumitem}

%%%%%%%% CODE RENDERING !!! UNCOMMENT IF NEEDED !!!
% Compile with flag -shell-escape
%\usepackage{minted}

%%%%%%%% START DOCUMENT

\title{SAUL Grammar}
\author{Juan Sebasti\'an C\'ardenas-Rodríguez \\
  \scalebox{0.7}{jscardenar@eafit.edu.co} \and
  Manuela Gallego Gómez \\
  \scalebox{0.7}{mgalle41@eafit.edu.co} \and
  \scalebox{0.7}{Mathematical Engineering, Universidad EAFIT}}

\date{\today}


\begin{document}
\maketitle

\section{Grammar}

The grammar accepted by SAUL is:
%
\begin{align*}
  \texttt{<program>}
  \equiv& \texttt{ codigo <funDefinitionList> fincodigo} \\
  \texttt{<funDefinitionList>}
  \equiv& \texttt{ <funDefinition> <funDefinitionList>} \mid \epsilon \\
  \texttt{<funDefinition>}
  \equiv& \texttt{ funcion <variable> ( <varDefList> )} \\
        & \texttt{ <varDefList> <statementList> fincodigo} \\
  \texttt{<varDefList>}
  \equiv& \texttt{ <variable> <varDefList>} \mid \epsilon \\
  \texttt{<variable>}
  \equiv& \texttt{ entero <variableName> } \mid \texttt{ real <variableName>} \\
  \texttt{<variableName>}
  \equiv& \texttt{ <letter> <characters>} \\
  \texttt{<letter>}
  \equiv&\,\,\, A \mid \ldots \mid Z \mid a \mid \ldots \mid z \\
  \texttt{<characters>}
  \equiv& \texttt{ <letter> <characters> } \mid
          \texttt{ <number> <characters> } \mid \epsilon \\
  \texttt{<number>}
  \equiv& \,\,\, 0 \mid \ldots \mid 9 \\
  \texttt{<statementList>}
  \equiv& \texttt{ <statement> <statementList>} \mid \epsilon \\
  \texttt{<statement>}
  \equiv& \texttt{ leer <variableName> } \\
  \mid& \texttt{ mostrar <variableName> } \\
  \mid& \texttt{ llamar <variableName> ( <variableList> ) } \\
  \mid& \texttt{ <variableName> = <mathExpression> } \\
  \texttt{<variableList>}
  \equiv& \texttt{ <variableName> <variableList> } \\
  \mid& \texttt{ <constant> <variableList>} \mid \epsilon \\
  \texttt{ <mathExpression> }
  \equiv& \texttt{ <variable>} \mid \texttt{ <constant> } \\
  \mid& \texttt{ ( \texttt{<mathExpression>} ) } \\
  \mid& \texttt{ <variable> <op> <mathExpression> } \\
  \mid& \texttt{ <constant> <op> <mathExpression> } \\
  \mid& \texttt{ ( <mathExpression> ) <op> <mathExpression> } \\
  \texttt{<constant>}
  \equiv& \texttt{ <numbers> } \mid \texttt{ <numbers>.<numbers> } \\
  \texttt{<numbers>}
  \equiv& \texttt{ <number><numbers> } \mid \texttt{ <number> } \\
  \texttt{ <op> }
  \equiv& \,\,\, + \mid - \mid * \mid /
\end{align*}

\section{Limitations}

The program must have a main function called ``principal'' that receives no
arguments.

The math operations must be written with a space between each term.

The grammar accepts only the four basic mathematical operations: addition,
subtraction, multiplication and division. Operations with parentheses are
performed first. Then, the standard order of operations is followed:
multiplication, division, addition and subtraction.

The math expressions only accept positive constants. In order to work with
negative values, the "read" statement or a math operation must be executed.

If a double value is assigned to an integer variable, an error is displayed.

There are no global variables. Local variables have a limited scope and cannot
be accessed outside the block in which they were declared.

\end{document}
